### 2021-05-10 papers/SYRCoSE/overview.tex
mention Equations plugin

>>>>

Encoding computable relations in \coq,
especially their (computable) transitive closures,
can be quite challenging since \coq is a total language and
its termination checker only understands termination patterns
going slightly beyond simple structural recursion.
To make it easier, we employ the \equations function definition plugin~%
\cite{Sozeau-Mangin:ICFP2019}
which provides both notations for writing programs by dependent pattern-matching
and good support for well-founded recursion.
